Data details

### 2024-07-20 analysis/data-details.qmd
unbritishize spelling

- **Cancel public events** (`c3_cancel_events`): Indicator of whether the country cancelled public events.
  - **0**: no measures; **1**: recommend cancelling; **2**: require cancelling; **Blank**: no data

>>>>

- **Cancel public events** (`c3_cancel_events`): Indicator of whether the country canceled public events.
  - **0**: no measures; **1**: recommend canceling; **2**: require canceling; **Blank**: no data
